Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
results montecarlo

\noindent 
Our solutions
is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines. The solution presented
by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. This one continues without being
integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. On the
other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications.
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

@@

@@

\subsection{Experiments}
\subsection{Results}

\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont2.png}
  \caption{Montecarlo execution time}
  \label{fig:internal}
\end{figure}
\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:internal}
\end{figure}

@@

\subsection{Experimental Results}
The test were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1090 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; the cloud platform is deployed by OpenStack; and
the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0b.
We have designed 6 different set-ups which can be divided
in 2 groups: “Exclusive GPUs” and “Shared GPUs”. The
“Exclusive” mode will provide, at most, 4 accelerators. Whilst
the number of available GPU in “Shared” mode will depend
on the partition size. In this particular case, we have halved
the memory, so we can use up to 8 GPUs. For each group, we
have deployed virtual clusters of 1, 2 and 3 nodes where will
run the processes of the application. The instances are based
on the flavor “m1.medium” which determines VM of 2 cores
and 4096 MB of memory.
MCUDA-MEME~\cite{Liu2010} has been the application executed with
different configurations in order to test the set-ups. MCUDA-
MEME is GPGPU MPI application, so the number of GPUs
will determine the number of executable processes.
The Figure~\ref{fig3} shows and compares the execution time of
the application with different configurations over different set-
ups. We can determine that with 1 node, the performance is
lower, with 2 and 3 is quite similar, though. Hence, the greatest
difference can be appreciated between modes, where the
highest performance is achieved by sharing the accelerators.

>>>>

\noindent

@@

\section{State of Art}
\label{sec:state}
Our solutions
is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines. The solution presented
by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. This one continues without being
integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. On the
other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications.
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

@@

\subsection{Experimental results}
In order to assess that GPU virtualization with AWS instances was working as expected, two applications were executed to analyze the results and their scalability.

The first of them was {\it Montecarlo Multigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.

% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:mont-opt}
\end{figure}

@@

\subsection{Experimental Results}
The test were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1090 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; the cloud platform is deployed by OpenStack; and
the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0.

We have designed 6 different set-ups which can be divided
in 2 groups: “Exclusive GPUs” and “Shared GPUs”. The
“Exclusive” mode will provide, at most, 4 accelerators. Whilst
the number of available GPU in “Shared” mode will depend
on the partition size. In this particular case, we have halved
the memory, so we can use up to 8 GPUs. For each group, we
have deployed virtual clusters of 1, 2 and 3 nodes where will
run the processes of the application. The instances are based
on the flavor “m1.medium” which determines VM of 2 cores
and 4096 MB of memory.

MCUDA-MEME~\cite{Liu2010} has been the application executed with
different configurations in order to test the set-ups. MCUDA-
MEME is GPGPU MPI application, so the number of GPUs
will determine the number of executable processes.
The Figure~\ref{fig3} shows and compares the execution time of
the application with different configurations over different set-
ups. We can determine that with 1 node, the performance is
lower, with 2 and 3 is quite similar, though. Hence, the greatest
difference can be appreciated between modes, where the
highest performance is achieved by sharing the accelerators.
